Should I AirBNB My Property?

### 2016-12-14 abbReturns_Script.Rmd
multiple bug fix

  spJoin <- over(rent.prop.shp, beach.buffer)
  ltr.data$beach <- ifelse(is.na(spJoin), 0 ,1)

@@

  abbtype.map <- ggplot() +
    geom_bar(data=abb.dataf, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    ggtitle('AirBNB Property Type\nBy Submarket')

@@

  ltrtype.map <- ggplot() +
    geom_bar(data=ltr.dataf, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    ggtitle('Long Term Property Type\nBy Submarket')

@@

  if(length(abba) > 0) abb.data <- abb.data[-abba, ]
  if(length(renta) > 0) ltr.data <- ltr.data[-renta, ]

>>>>

  spJoin <- over(ltr.prop.shp, beach.buffer)
  ltr.data$beach <- ifelse(is.na(spJoin), 0 ,1)

@@

  abbtype.map <- ggplot() +
    geom_bar(data=abb.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    ggtitle('AirBNB Property Type\nBy Submarket')

@@

  ltrtype.map <- ggplot() +
    geom_bar(data=ltr.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    ggtitle('Long Term Property Type\nBy Submarket')

@@

  if(length(abba) > 0) abb.data <- abb.data[-abba, ]
  if(length(ltra) > 0) ltr.data <- ltr.data[-ltra, ]
